\documentclass[a4paper, landscape]{article}

\input{include/cardLibs.tex}
\input{include/cardColours.tex}
\input{include/cardStyles.tex}

\begin{document}
\pagestyle{empty}

\begin{center}
\greycard{Private Eye}{WATSON!!!}{
	At the end of the game, before anyone else reveals their cards, you must
	publicly announce the identity of the buried card. If correct, you win.
	If incorrect, you lose.
}
\greycard{Gambler}{It's all or nothing}{
	Before the last round begins, you must publicly announce which team
	you think is going to win. If you are correct, you win. If not, you
	lose.
} 
\greycard{Hot Potato}{Hot, hot, hot!!!}{
	You lose at the end of the game
	\\\vspace{0.5cm} 
	Any player that card shares or color shares with you must immediately
	trade cards with you: You gain their card, and assume their previous
	role. The other player becomes the Hot Potato.
} 
\greycard{Born Leader}{Born to lead!}{
	You win if you are a \character{Leader} at the end of the game.
} 
\greycard{Born Leader}{Born to lead!}{
	You win if you are a \character{Leader} at the end of the game.
}
\greycard{Born Leader}{Born to lead!}{
	You win if you are a \character{Leader} at the end of the game.
}
\greycard{Anarchist}{I like to watch the world burn!}{
	You win if you helped overthrow a \character{Leader} in the majority of
	rounds.
}
\greycard{Minion}{Master must always lead!}{
	You win if a \character{Leader} is never overthrown in the same room as
	you.
}
\end{center}

\backpanel
\newpage

\begin{center}
\greycard{Telepath}{See into the future...}{
	Before the last hostage exchange, you must publicly announce that you
	are the \character{Telepath} and predict which player is coming into
	your current room. You win if you are correct.
}
\purplecard{Amnesiac}{Whose team am I on again???}{
	At the end of the game, before anyone else reveals their cards, you must
	declare which team you are on by saying, ``I remember which team I am
	on. I am on team ...''. Choosing either: The blue team, the red team, or
	nobody's team. If you choose the team with a minority of players (or
	picked nobody's team in case of a tie), you win.
}
\end{center}

\backpanel

% \mixedcard{Mastermind}{Know it all!}{At the end of the game, before anyone
% reveal their cards, you must publicly announce the colour of \emph{every}
% player. If correct, you win and everyone else loses.\\\vspace{0.3cm} You can
% use either colour for Colour Share or Reveal.}

\end{document}
