\documentclass[a4paper, landscape]{article}

\input{include/cardLibs.tex}
\input{include/cardColours.tex}
\input{include/cardStyles.tex}

\begin{document}
\pagestyle{empty}
\begin{center}

\greycard{Ahab}{Ahoy Matey!}{
	You win if \character{Moby} gains the \condition{dead} condition, and
	you do not.
} 
\greycard{Moby}{Splash...}{
	You win if \character{Ahab} gains the \condition{dead} condition, and
	you do not.
}
\greycard{Wife}{First-lady.}{
	You win if you are in the same room as the \character{President} at the
	end of the game, and the \character{Mistress} is not.
} 
\greycard{Mistress}{The other woman.}{
	You win if you are in the same room as the \character{President} at the
	end of the game, and the \character{Wife} is not.
}
\greycard{Frotteur}{Can't keep your hands to yourself!}{
	If you touch every player by the end of the game, you win.
	\\\vspace{0.5cm} 
	If the \character{Prude} grabs your wrist, you lose.
} 
\greycard{Prude}{Don't let go, no matter what!}{
	You win if you grab the wrist of the \character{Frotteur}. You may only
	grab the wrist of one player per game.
	\\\vspace{0.5cm} 
	Once you grab a wrist, you must hold on until the end of the game. You
	and the person you have grabbed cannot be seperated: you must both be
	hostages, or neither of you.
}
\greycard{Juliet}{Find that boy!}{
	You win if you are in the same room as \character{Romeo} and you both
	gain the \condition{dead} condition at the end of the game.
} 
\greycard{Romeo}{Find that girl!}{
	You win if you are in the same room as \character{Juliet} and you both
	gain the \condition{dead} condition at the end of the game.
} 

\backpanel
\newpage

\greycard{Sniper}{One shot. One kill.}{
	At the end of the game, before anyone reveals their cards, you must
	publicly announce any one player in the game to shoot. The selected
	player does not have to be in the same room as you. You win if you shoot
	the \character{Target}.
	\\\vspace{0.25cm} 
	The shot player gains the \condition{dead} condition. This triggers
	backup characters, if available. Note: a dead bomber does not detonate.
} 
\greycard{Target}{Keep it secret, keep it safe!}{
	You win if the \character{Sniper} does not shoot you at the end of the
	game.
} 
\greycard{Decoy}{Look like a big red dot!}{
	You win if the \character{Sniper} shoots you at the end of the game.
} 
\greycard{Rock}{You're rocky...}{
	You win if you are in the same room as \character{Scissors} at the end
	of the game, and \character{Paper} is not.
} 
\greycard{Paper}{You're papery...}{
	You win if you are in the same room as \character{Rock} at the end of
	the game, and \character{Scissors} is not.
} 
\greycard{Scissors}{You're sharp...}{
	You win if you are in the same room as \character{Paper} at the end of
	the game, and \character{Rock} is not.
}
\greycard{Butler}{At your service.}{
	You win if you are in the same room as the \character{Maid} and
	\character{President} at the end of the game.
} 
\greycard{Maid}{At your service.}{
	You win if you are in the same room as the \character{Butler} and
	\character{President} at the end of the game.
} 

\backpanel
\newpage

\greycard{Rival}{My Nemesis!!!!}{
	You win if you are \emph{not} in the same room as the
	\character{President} when the game ends.
} 
\greycard{Survivor}{I'm a survivor,\\ I'm not gon' give up...}{
	You win if you do not gain the \condition{dead} condition.
} 
\greycard{Intern}{Do your best!}{
	You win if you are in the same room as the \character{President} when
	the game ends.
} 
\greycard{Anarchist}{I like to watch the world burn!}{
	You win if you helped overthrow a \character{Leader} in the majority of
	rounds.
}
\greycard{Minion}{Master must always lead!}{
	You win if a \character{Leader} is never overthrown in the same room as
	you.
}
\greycard{Victim}{That bomb's got your name on it!}{
	You win if you gain the \condition{dead} condition due to the Bomber
	exploding.
} 

\backpanel


\end{center}
\end{document}
